\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\definecolor{bodytext}{HTML}{444444}
\definecolor{heading}{HTML}{000000}

\color{bodytext}

% Page layout
\geometry{margin=1in}
\pagestyle{fancy}
\fancyhf{}

% Footer with watermark note
\fancyfoot[C]{%
  \textcolor{bodytext}{\tiny\textsuperscript{1}This résumé is open-source and written in \LaTeX{} – \href{https://github.com/i-st04/resume}{GitHub Project \faExternalLink*}}
}

\renewcommand{\footrulewidth}{0.4pt}
\renewcommand{\headrulewidth}{0pt}

% Section title formatting for unnumbered sections
\titleformat{name=\section,numberless}
  {\filcenter\Large\sffamily\bfseries\uppercase}{}{0em}{}[\vspace{1em}]

\titleformat{name=\subsection,numberless}[runin]
  {\sffamily\bfseries}{\hspace{-1em}}{0pt}{}[ \hfill]

\titleformat{name=\subsubsection,numberless}[runin]
  {\sffamily\small\bfseries}{}{0pt}{}[ -- \\]

\titlespacing{\subsection}{0pt}{0.1em}{0em}
\titlespacing{\subsubsection}{0pt}{0.2em}{0.2em}

% Remove extra spacing in itemize
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

% Name and contact formatting
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries \theauthor} \\[0.3em]
    {\large\sffamily Junior Web developer} \\[0.3em]
    \small\sffamily
    Dunavskih virova 08, Belgrade \textbullet{}
    \href{tel:+381644745664}{(+381) 64 4745664} \textbullet{}
    \href{mailto:ivona.stankovic04@gmail.com}{ivona.stankovic04@gmail.com} \\[0.75em]
    
    \textcolor{bodytext}{
      {\footnotesize GitHub:} \href{https://github.com/i-st04}{i-st04~\textcolor{gray}{\faExternalLink*}} \quad |
      {\footnotesize LinkedIn:} \href{https://www.linkedin.com/in/ivona-stanković-724b0935a/}{Ivona Stankovic ~\textcolor{gray}{\faExternalLink*}} \quad
    }
  \end{center}
  \vspace{1em}
  \hrule
  \vspace{0em}
}

\title{Résumé}
\author{Ivona Stankovic}
\date{}

\begin{document}

\maketitle

\section*{Education}

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Electrical Engineering High School "Nikola Tesla" & Sep 2019 -- May 2023
  \end{tabular*}
}
\textbf{Major:} Network and System Administration

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Cubes School & Oct 2023 -- Oct 2024
  \end{tabular*}
}
\textbf{Specialization:} JavaScript and React.js Development Course

\section*{Skills}

\subsubsection*{Languages}

\par

\noindent
\begin{minipage}{\linewidth}
\begin{tabular}{@{}ll}
\textbf{Programming:}   & JavaScript, TypeScript \\
\textbf{Libraries:}     & React.js \\
\textbf{Markup:}        & HTML5, \LaTeX \\
\textbf{Stylesheet:}    & CSS \\
\textbf{Preprocessors:} & SASS \\
\textbf{Frameworks:}    & Bootstrap, Next.js, Vue.js \\
\end{tabular}
\end{minipage}

\section*{Work Experience}

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Viver Caffé Playground | Kids Animator & Nov 2022 -- May 2023
  \end{tabular*}
}
\begin{itemize}
  \item Supervised and cared for children in the playground; collaborated with a team of colleagues to ensure safe and engaging activities for up to 50 children.
  \item Maintained cleanliness and addressed any issues within and around the playground.
\end{itemize}

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Viver Caffé Playground | Info Desk & Nov 2022 -- Mar 2023
  \end{tabular*}
}
\begin{itemize}
  \item Managed birthday party and event reservations.
  \item Sold playground tickets and coordinated catering for celebrations.
\end{itemize}

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Princess Puff's d.o.o | Retail Assistant & Aug 2023
  \end{tabular*}
}
\begin{itemize}
  \item Sold puff doughnuts in one of Belgrade’s largest shopping malls.
  \item Maintained a clean and sanitary workspace to ensure a professional experience for customers.
\end{itemize}

\subsection*{
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l r}
    Cubes d.o.o | Internship – Web Developer & Jan 2025 -- Jul 2025
  \end{tabular*}
}
\textit{Hybrid}\\
\textbf{Overview:} After completing a course at Cubes School, I was offered an internship based on my performance. This was my first real-world experience applying programming knowledge in a team setting.

\textbf{Feb – Mar 2025 | Project: \textit{Magical Oasis (Next.js E-commerce Site)}}
\begin{itemize}
  \item Contributed to building an e-commerce store for children’s toys from the ground up as part of a 3-person team.
  \item Implemented secure user authentication and authorization using NextAuth.js, ensuring safe login, registration, and product saving features.
  \item Built a fully functional shopping cart and checkout process with smooth and enjoyable user experience.
  \item Followed clean code principles and reused components to maintain a scalable and maintainable codebase.
\end{itemize}

\textbf{Mar – Jul 2025 | Mtel Switzerland}
\begin{itemize}
  \item Took part ownership of front-end development for a large-scale telecom platform, collaborating with a mentor who handled checkout logic while I focused on component architecture, page structure, and UI behavior.
  \item Built multilingual pages and SEO-friendly sitemap views using \texttt{next-intl}, applying internationalization best practices across both desktop and mobile self-care interfaces.
  \item Created an interactive map component using \texttt{react-google-maps} integrated with a Swiper carousel.
  \item Developed dynamic, scroll-responsive UI sections using \texttt{IntersectionObserver} and \texttt{ResizeObserver}.
  \item Implemented a responsive carousel system that adapted its movement based on screen width and disabled navigation buttons when reaching the end of the scroll range.
  \item Refactored layout and DOM structure to support consistent animation triggers, scroll tracking, and hydration-safe rendering in Next.js.
  \item Applied clean code principles and reusable logic patterns to maintain a scalable codebase, participating in code reviews and adapting quickly to production workflows.
  \item Enjoyed collaborating closely with my colleagues throughout the project; although my internship concluded before its completion, I gained valuable experience contributing to key milestones.
\end{itemize}

\end{document}
